Case Study: 16S microbiome data (Schubert et al., 2014)

### 2018-05-10 datasets/ChIP-seq/ChIPseq-CBP-csaw.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

## project data/results folders
datdir <- "data"
resdir <- "results"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(resdir, "cbp-csaw-counts.rds")
filtered_file <- file.path(resdir, "cbp-csaw-counts-filtered.rds")
normfacs_file <- file.path(resdir, "cbp-csaw-counts-normfacs.rds")
result_file <- file.path(resdir, "cbp-csaw-results.rds")
bench_file <- file.path(resdir, "cbp-csaw-benchmark.rds")

>>>>

## project data/results folders
datdir <- "data"
resdir <- "results"
sbdir <- "../../results/ChIPseq"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)
dir.create(sbdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(resdir, "cbp-csaw-counts.rds")
filtered_file <- file.path(resdir, "cbp-csaw-counts-filtered.rds")
normfacs_file <- file.path(resdir, "cbp-csaw-counts-normfacs.rds")
result_file <- file.path(resdir, "cbp-csaw-results.rds")
bench_file <- file.path(sbdir, "cbp-csaw-benchmark.rds")

### 2018-05-10 datasets/ChIP-seq/ChIPseq-h3k4me3-csaw.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

## project data/results folders
datdir <- "data"
resdir <- "results"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(resdir, "h3k4me3-csaw-counts.rds")
filtered_file <- file.path(resdir, "h3k4me3-csaw-counts-filtered.rds")
result_file <- file.path(resdir, "h3k4me3-csaw-results.rds")
bench_file <- file.path(resdir, "h3k4me3-csaw-benchmark.rds")

>>>>

## project data/results folders
datdir <- "data"
resdir <- "results"
sbdir <- "../../results/ChIPseq"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)
dir.create(sbdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(resdir, "h3k4me3-csaw-counts.rds")
filtered_file <- file.path(resdir, "h3k4me3-csaw-counts-filtered.rds")
result_file <- file.path(resdir, "h3k4me3-csaw-results.rds")
bench_file <- file.path(sbdir, "h3k4me3-csaw-benchmark.rds")

### 2018-05-10 datasets/ChIP-seq/ChIPseq-h3k4me3-promoters.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

## project data/results folders
datdir <- "data"
resdir <- "results"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(resdir, "h3k4me3-promotors-counts.rds")
result_file <- file.path(resdir, "h3k4me3-promotors-results.rds")
bench_file <- file.path(resdir, "h3k4me3-promotors-benchmark.rds")

>>>>

## project data/results folders
datdir <- "data"
resdir <- "results"
sbdir <- "../../results/ChIPseq"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)
dir.create(sbdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(resdir, "h3k4me3-promotors-counts.rds")
result_file <- file.path(resdir, "h3k4me3-promotors-results.rds")
bench_file <- file.path(sbdir, "h3k4me3-promotors-benchmark.rds")

### 2018-05-10 datasets/RNA-Seq/RNAseq-gtex.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

## project data/results folders
datdir <- "data"
resdir <- "results"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(datdir, "brain-counts.rds")
result_file <- file.path(resdir, "brain-results.rds")
bench_file <- file.path(resdir, "brain-benchmark.rds")

>>>>

## project data/results folders
datdir <- "data"
resdir <- "results"
sbdir <- "../../results/RNAseq"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)
dir.create(sbdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(resdir, "brain-counts.rds")
result_file <- file.path(resdir, "brain-results.rds")
bench_file <- file.path(sbdir, "brain-benchmark.rds")

### 2018-05-10 datasets/RNA-Seq/RNAseq-mir200c.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

## project data/results folders
datdir <- "data"
resdir <- "results"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(datdir, "rse_gene.Rdata")
result_file <- file.path(resdir, "mir200c-results.rds")
bench_file <- file.path(resdir, "mir200c-benchmark.rds")

>>>>

## project data/results folders
datdir <- "data"
resdir <- "results"
sbdir <- "../../results/RNAseq"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

## intermediary files we create below
count_file <- file.path(resdir, "rse_gene.Rdata")
result_file <- file.path(resdir, "mir200c-results.rds")
bench_file <- file.path(sbdir, "mir200c-benchmark.rds")

### 2018-05-10 datasets/RNA-Seq/polyester-simulation.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

```{r workspace-setup, results='hide', message=FALSE, warning=FALSE}
# Load packages needed to simulate RNA-seq counts with polyester
library(zebrafishRNASeq) 
library(genefilter)
library(limma)
library(polyester)

# Differential testing
library(DESeq2)

# Load supporting packages for data analyses
library(data.table)
library(magrittr)
library(dplyr)
library(ggplot2)
library(R.utils)
library(cowplot)
library(tibble)
library(ggthemes)

# benchmark methods
library(IHW)
library(ashr)
library(qvalue)
library(swfdr)
library(fdrtool)
# Installed BayesLogit from CRAN archive via `R CMD INSTALL BayesLogit_0.6.tar.gz`
# install_github('jgscott/FDRreg', subdir="R_pkg/")
library(FDRreg)

# comparison tools/functions
# devtools::install_github("areyesq89/SummarizedBenchmark", ref="fdrbenchmark") # needed b/c BioC devel branch is 
library(SummarizedBenchmark)

# load helper functions
sourceDirectory(file.path("../R/"))

@@

if (!file.exists(file.path("polyester-results-null5.RDS"))){
  null5 <- bplapply(X=1:B, FUN=simulateOneSplit, counts=counts,
                   paramPolyester=params, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   BPPARAM=multicoreParam)
  saveRDS(null5, file=file.path("polyester-results-null5.RDS"))
} else {
  null5 <- readRDS(file=file.path("polyester-results-null5.RDS"))
}
```

@@

if (!file.exists(file.path("polyester-results-null10.RDS"))){
  null10 <- bplapply(X=1:B, FUN=simulateOneSplit, counts=counts,
                   paramPolyester=params, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   BPPARAM=multicoreParam)
  saveRDS(null10, file=file.path("polyester-results-null10.RDS"))
} else {
  null10 <- readRDS(file=file.path("polyester-results-null10.RDS"))
}
```

@@

if (!file.exists(file.path("polyester-results-de5.RDS"))){
  de5 <- bplapply(X=1:B, FUN=simulateOneSplit, counts=counts,
                   paramPolyester=params, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   BPPARAM=multicoreParam)
  saveRDS(de5, file=file.path("polyester-results-de5.RDS"))
} else {
  de5 <- readRDS(file=file.path("polyester-results-de5.RDS"))
}
```

@@

if (!file.exists(file.path("polyester-results-de10.RDS"))){
  de10 <- bplapply(X=1:B, FUN=simulateOneSplit, counts=counts,
                   paramPolyester=params, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   BPPARAM=multicoreParam)
  saveRDS(de10, file=file.path("polyester-results-de10.RDS"))
} else {
  de10 <- readRDS(file=file.path("polyester-results-de10.RDS"))
}
```

>>>>

```{r workspace-setup, results='hide', message=FALSE, warning=FALSE}
# Load packages needed to simulate RNA-seq counts with polyester
library(SummarizedBenchmark)
library(zebrafishRNASeq) 
library(genefilter)
library(limma)
library(polyester)
library(DESeq2)
library(data.table)
library(magrittr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tibble)
library(ggthemes)

# load helper functions
for (f in list.files("../R", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

# set up results directories 
resdir <- "../../results/RNAseq"
dir.create(resdir, showWarnings = FALSE)

# results files that will be generated below
resfile_n5 <- file.path(resdir, "polyester-results-null5.rds")
resfile_n10 <- file.path(resdir, "polyester-results-null10.rds")
resfile_d5 <- file.path(resdir, "polyester-results-de5.rds")
resfile_d10 <- file.path(resdir, "polyester-results-de10.rds")

@@

if (!file.exists(resfile_n5)){
  null5 <- bplapply(X=1:B, FUN=simulateOneSplit, counts=counts,
                   paramPolyester=params, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   BPPARAM=multicoreParam)
  saveRDS(null5, file=resfile_n5)
} else {
  null5 <- readRDS(file=resfile_n5)
}
```

@@

if (!file.exists(resfile_n10)){
  null10 <- bplapply(X=1:B, FUN=simulateOneSplit, counts=counts,
                   paramPolyester=params, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   BPPARAM=multicoreParam)
  saveRDS(null10, file=resfile_n10)
} else {
  null10 <- readRDS(file=resfile_n10)
}
```

@@

if (!file.exists(resfile_d5)){
  de5 <- bplapply(X=1:B, FUN=simulateOneSplit, counts=counts,
                   paramPolyester=params, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   BPPARAM=multicoreParam)
  saveRDS(de5, file=resfile_d5)
} else {
  de5 <- readRDS(file=resfile_d5)
}
```

@@

if (!file.exists(resfile_d10)){
  de10 <- bplapply(X=1:B, FUN=simulateOneSplit, counts=counts,
                   paramPolyester=params, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   BPPARAM=multicoreParam)
  saveRDS(de10, file=resfile_d10)
} else {
  de10 <- readRDS(file=resfile_d10)
}
```

### 2018-05-10 datasets/RNA-Seq/yeast-simulation.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

```{r, results='hide', message=FALSE}
# Load packages and source benchmark FDR
library(data.table)
library(tidyr)
library(dplyr)
library(readr)
library(ggplot2)
library(magrittr)
library(cowplot)
library(purrr)
library(DESeq2)
library(tibble)
library(ggthemes)
library(R.utils)

@@

# set up data / results directories
datdir <- "yeast-data"
resdir <- "yeast-results"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

@@

```{r, results='hide', message=FALSE}
rseed <- 225
sampleSize <- 5
nDE <- 0
resfile <- file.path(resdir, "null5.rds")

if (!file.exists(resfile)){
  null5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null5, file=resfile)
}else{
  null5 <- readRDS(file=resfile)
}

@@

```{r, results='hide', message=FALSE}
rseed <- 837
sampleSize <- 10
nDE <- 0
resfile <- file.path(resdir, "null10.rds")

if (!file.exists(resfile)){
  null10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null10, file=resfile)
}else{
  null10 <- readRDS(file=resfile)
}

@@

```{r, results='hide', message=FALSE}
rseed <- 198
sampleSize <- 5
nDE <- 500
resfile <- file.path(resdir, "de5.rds")

if (!file.exists(resfile)){
  de5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de5, file=resfile)
}else{
  de5 <- readRDS(file=resfile)
}
```

@@

```{r, results='hide', message=FALSE}
rseed <- 961
sampleSize <- 10
nDE <- 500
resfile <- file.path(resdir, "de10.rds")

if(!file.exists(resfile)){
  de10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de10, file=resfile)
}else{
  de10 <- readRDS(file=resfile)
}
```

>>>>

```{r, results='hide', message=FALSE}
# Load packages and source benchmark FDR
library(SummarizedBenchmark)
library(data.table)
library(tidyr)
library(dplyr)
library(readr)
library(ggplot2)
library(magrittr)
library(cowplot)
library(purrr)
library(DESeq2)
library(tibble)
library(ggthemes)
library(R.utils)

@@

# set up data / results directories
datdir <- "yeast-data"
resdir <- "../../results/RNAseq"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

# results files that will be generated
resfile_n5 <- file.path(resdir, "yeast-results-null5.rds")
resfile_n10 <- file.path(resdir, "yeast-results-null10.rds")
resfile_d5 <- file.path(resdir, "yeast-results-de5.rds")
resfile_d10 <- file.path(resdir, "yeast-results-de10.rds")

@@

```{r, results='hide', message=FALSE}
rseed <- 225
sampleSize <- 5
nDE <- 0

if (!file.exists(resfile_n5)){
  null5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null5, file = resfile_n5)
}else{
  null5 <- readRDS(file = resfile_n5)
}

@@

```{r, results='hide', message=FALSE}
rseed <- 837
sampleSize <- 10
nDE <- 0

if (!file.exists(resfile_n10)){
  null10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null10, file = resfile_n10)
}else{
  null10 <- readRDS(file = resfile_n10)
}

@@

```{r, results='hide', message=FALSE}
rseed <- 198
sampleSize <- 5
nDE <- 500

if (!file.exists(resfile_d5)){
  de5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de5, file = resfile_d5)
}else{
  de5 <- readRDS(file = resfile_d5)
}
```

@@

```{r, results='hide', message=FALSE}
rseed <- 961
sampleSize <- 10
nDE <- 500

if(!file.exists(resfile_d10)){
  de10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de10, file = resfile_d10)
}else{
  de10 <- readRDS(file = resfile_d10)
}
```

### 2018-05-10 datasets/microbiome/microbiome-baxter.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

## project data/results folders
datdir <- "data"
resdir <- "results"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

@@

otu_result_file <- file.path(resdir, "baxter-otus-results.rds")
otu_bench_file <- file.path(resdir, "baxter-otus-benchmark.rds")
otu_bench_file_log_ubiquity <- file.path(resdir, "baxter-otus-log-ubiquity-benchmark.rds")

gns_result_file <- file.path(resdir, "baxter-genus-results.rds")
gns_bench_file <- file.path(resdir, "baxter-genus-benchmark.rds")
gns_bench_file_log_ubiquity <- file.path(resdir, "baxter-genus-log-ubiquity-benchmark.rds")
```

@@

@@

@@

```{r, baxter-genus-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```

>>>>

## project data/results folders
datdir <- "data"
resdir <- "results"
sbdir <- "../../results/microbiome"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)
dir.create(sbdir, showWarnings = FALSE)

@@

otu_result_file <- file.path(resdir, "baxter-otus-results.rds")
otu_bench_file <- file.path(sbdir, "baxter-otus-benchmark.rds")
otu_bench_file_log_ubiquity <- file.path(sbdir, "baxter-otus-log-ubiquity-benchmark.rds")

gns_result_file <- file.path(resdir, "baxter-genus-results.rds")
gns_bench_file <- file.path(sbdir, "baxter-genus-benchmark.rds")
gns_bench_file_log_ubiquity <- file.path(sbdir, "baxter-genus-log-ubiquity-benchmark.rds")
```

@@

```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r, eval=FALSE}
assays(sb)[["qvalue"]][, "ashq"] %>% max()
sum(is.na(assays(sb)[["qvalue"]][, "scott-empirical"]))
sum(is.na(assays(sb)[["qvalue"]][, "lfdr"]))
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r, baxter-genus-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

### 2018-05-10 datasets/microbiome/microbiome-enigma.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

## project data/results folders
datdir <- "data"
resdir <- "results"
enigma_dir <- file.path(datdir, "enigma_results")

# From their paper, we expect SO4 to have little correlation, pH
# to have high correlations, and Al to be in the middle
so4_result_file <- file.path(resdir, "enigma-so4-otus-results.rds")
so4_bench_file <- file.path(resdir, "enigma-so4-otus-benchmark.rds")

ph_result_file <- file.path(resdir, "enigma-ph-otus-results.rds")
ph_bench_file <- file.path(resdir, "enigma-ph-otus-benchmark.rds")

al_result_file <- file.path(resdir, "enigma-al-otus-results.rds")
al_bench_file <- file.path(resdir, "enigma-al-otus-benchmark.rds")
```

@@

```{r, ph-plot, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```

@@

```{r, so4-plot, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```

@@

```{r, al-plot, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```

>>>>

## project data/results folders
datdir <- "data"
resdir <- "results"
sbdir <- "../../results/microbiome"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)
dir.create(sbdir, showWarnings = FALSE)

enigma_dir <- file.path(datdir, "enigma_results")
dir.create(enigma_dir, showWarnings = FALSE)

# From their paper, we expect SO4 to have little correlation, pH
# to have high correlations, and Al to be in the middle
so4_result_file <- file.path(resdir, "enigma-so4-otus-results.rds")
so4_bench_file <- file.path(sbdir, "enigma-so4-otus-benchmark.rds")

ph_result_file <- file.path(resdir, "enigma-ph-otus-results.rds")
ph_bench_file <- file.path(sbdir, "enigma-ph-otus-benchmark.rds")

al_result_file <- file.path(resdir, "enigma-al-otus-results.rds")
al_bench_file <- file.path(sbdir, "enigma-al-otus-benchmark.rds")
```

@@

```{r, ph-plot, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r, so4-plot, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r, al-plot, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

### 2018-05-10 datasets/microbiome/microbiome-goodrich.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

otu_result_file <- file.path(resdir, "goodrich-otus-results.rds")
otu_bench_file <- file.path(resdir, "goodrich-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "goodrich-genus-results.rds")
gns_bench_file <- file.path(resdir, "goodrich-genus-benchmark.rds")
```

@@

```{r, goodrich-plot, width=15, height=15, eval=TRUE}
## plot nrejects by method overall and stratified by covariate
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
##plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE )
```

@@

```{r, goodrich-genus-plot, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```

>>>>

otu_result_file <- file.path(resdir, "goodrich-otus-results.rds")
otu_bench_file <- file.path(sbdir, "goodrich-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "goodrich-genus-results.rds")
gns_bench_file <- file.path(sbdir, "goodrich-genus-benchmark.rds")
```

@@

```{r, goodrich-plot, width=15, height=15, eval=TRUE}
## plot nrejects by method overall and stratified by covariate
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
##plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE )
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r, goodrich-genus-plot, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

### 2018-05-10 datasets/microbiome/microbiome-papa.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

otu_result_file <- file.path(resdir, "papa-otus-results.rds")
otu_bench_file <- file.path(resdir, "papa-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "papa-genus-results.rds")
gns_bench_file <- file.path(resdir, "papa-genus-benchmark.rds")
gns_bench_file_log_ubi <- file.path(resdir, "papa-genus-log-ubiquity-benchmark.rds")
```

@@

```{r, eval=FALSE}
assays(sb)[["qvalue"]][, "ashq"] %>% max()
sum(is.na(assays(sb)[["qvalue"]][, "scott-empirical"]))
sum(is.na(assays(sb)[["qvalue"]][, "lfdr"]))
```

@@

```{r, papa-genus-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```

@@

```{r, papa-genus-logubi-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```

>>>>

otu_result_file <- file.path(resdir, "papa-otus-results.rds")
otu_bench_file <- file.path(sbdir, "papa-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "papa-genus-results.rds")
gns_bench_file <- file.path(sbdir, "papa-genus-benchmark.rds")
gns_bench_file_log_ubi <- file.path(resdir, "papa-genus-log-ubiquity-benchmark.rds")
```

@@

```{r, eval=FALSE}
assays(sb)[["qvalue"]][, "ashq"] %>% max()
sum(is.na(assays(sb)[["qvalue"]][, "scott-empirical"]))
sum(is.na(assays(sb)[["qvalue"]][, "lfdr"]))
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r, papa-genus-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r, papa-genus-logubi-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

### 2018-05-10 datasets/microbiome/microbiome-schubert.Rmd
Save ChIPseq, RNAseq, and microbiome results to common dir
Also add covariateLinePlots to microbiome Rmds.

otu_result_file <- file.path(resdir, "schubert-otus-results.rds")
otu_bench_file <- file.path(resdir, "schubert-otus-benchmark.rds")
```

@@

```{r, schubert-plot, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```

>>>>

otu_result_file <- file.path(resdir, "schubert-otus-results.rds")
otu_bench_file <- file.path(sbdir, "schubert-otus-benchmark.rds")
```

@@

```{r, schubert-plot, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```
